\pagebreak
\section{WEEK8-More on SQL}
 
\begin{enumerate}
    \item Aggregation operators\begin{enumerate}
        
    \item What's Aggregation operators: Operations that apply to entire columns and produce a single result.
    \item Covered in this course: Grouping Operator： AVG() COUNT() MIN() MAX() SUM().
    \item GROUP BY : \begin{itemize}
        \item followed SFW
        \item Result will be grouped by the values of attributes in GROUP BY. All the AGG will only apply to each group of data.
    \end{itemize}
    \item If using any Aggregation, all the elements must be Aggregated or An attribute on the GROUP BY list.
    \item HAVING ：Same as WHERE but let you decide which groups to keep. (the attribute in HAVING must be either a grouping attribute or aggregated attribute
    \item NULL: NULL values are not contributes to a sum average or count and never be the min or max unless all values are NULL.
    \item which means, if a aggregation is apply to all NULL values then the result will be NULL, except COUNT will be zero.
    \item DISTINT: DISTINT will be proceed before the aggregation!.
    \end{enumerate}
    \item BAG and SET \begin{enumerate}
    \item UNION INTERSECT EXCEPT: have to use Bracket between two queries.
    \item force to SET: using DISTINT will force the result became a SET.(SELECT DISTINCT)
    \item  Rules for set:
    \begin{itemize}
        \item UNION: A UNION B A + B without any duplicates
        \item INTERSECTION: A INTERSECT B common elements in both A and B
        \item EXCEPT: A EXCEPT B elements that in  not in B
    \end{itemize}
    
    \item force to BAG: using ALL will force the result became a BAG.(SELECT (a) UNION ALL (b))
    \item Rules for bag:
    \begin{itemize}
        \item UNION: A UNION B All elements in A and in B WITH duplicates
        \item INTERSECTION: A INTERSECT B common elements with minimum number in each of subquery
        \item EXCEPT: A EXCEPT B A-B the number of elements will never goes to negative.
        \item to sum up: When you consider about bag, just think that elements with same value are difference.
    \end{itemize}
    \end{enumerate}
    \item Database Modifications:
    \begin{enumerate}
        \item Insert \begin{itemize}
            \item INSERT INTO Target relation) values;
            \item values could be a result of a query.
            \item Date insertion: \begin{itemize}
                \item Default format: 'YYYY-MM-DD'
                \item Format that also works: 'DD-Mon-YYYY'
                \item TO\_DATA(str,format)
            \end{itemize}
        \end{itemize}
        \item Deletetion:
            DELETE FROM (Relation) WHERE (Condition)
        \item Update: UPDATE (relation) SET a=a b=b c=c WHERE (Conditions).
    \end{enumerate}
    
\end{enumerate}
